\addcontentsline{toc}{chapter}{\protect Curriculum Vitae}
\markboth{Curriculum Vitae}{Curriculum Vitae}


\chapter*{Curriculum Vitae}

{\it European Southern Observatory\\
Karl-Schwarzschild-str. 2\\
D-85748, Germany} \\
+49 (0)89 3200 6672\\

\parindent 0pt 

{\bf Email:} sthabile.kolwa@gmail.com\\
{\bf Nationality:} South African\\
{\bf Languages:} English (native), Lozi (native), French (basic), German (basic)\\

\vspace*{1cm}

{\bf \Large Education} \\[1.5ex]
\normalsize{\bf Aug 2016 - present:}\\
{\bf Doctorate Degree (Dr. rer. nat.), Physics},\\
 Ludwig-Maximilians-Universit\"at M\"unchen\\
Expected date of completion: December 2019 \\ 
European Southern Observatory (ESO) \\
Title: {\it Baryons in the circumgalactic gas of high-redshift radio galaxies}\\
Advisor: Dr. Carlos de Breuck, co-advisor: Dr. Jo\"el Vernet

\vspace*{0.6cm}

\normalsize{\bf Past:}\\
{\bf M.Sc. Physics, Cum Laude},\\
 University of the Western Cape (UWC), 2016 \\				
Title: {\it The Effects of Environment on radio-loud AGN Activity in Stripe 82}\\
Advisor: Prof. Dr. Matt J. Jarvis, co-advisor: Dr. Kim McAlpine\\

{\bf B.Sc. Honours Astrophysics and Physics},\\
University of Cape Town (UCT), 2013 \\
National Astrophysics and Space Sciences Program (NASSP)

\vspace*{1cm}

{\bf \Large Refereed Publications:}\\[1.5ex]
\normalsize{\bf As a first author:}\\ [0.5ex]
{\bf S. Kolwa}, J. Vernet, C. De Breuck, M. Villar-Mart\'in, A. Humphrey, F. Arrigoni-Battaia, B. Gullberg, T. Falkendal, G. Drouart, M. D. Lehnert, D. Wylezalek, and A. Man (2019)\\ 
\href{http://adsabs.harvard.edu/abs/2019arXiv190405114K}{arXiv:1904.05114 }\\
{\it MUSE unravels the ionization and origin of metal enriched absorbers in the gas halo of a $z = 2.92$ radio galaxy}\\
\\
{\bf S. Kolwa}, M. J. Jarvis, K. McAlpine, and I. Heywood (2019) \href{http://adsabs.harvard.edu/abs/2019MNRAS.482.5156K}{MNRAS, 482, 5156-5166} \\
{\it The relation between galaxy density and radio jet power for 1.4 GHz VLA selected AGN in Stripe 82} \\

\normalsize{\bf As a co-author:}\\ [0.5ex]
Theresa Falkendal, Carlos De Breuck, Matthew D. Lehnert, Guillaume Drouart, Jo\"el Vernet, Bjorn Emonts, Minju Lee, Nicole P. H. Nesvadba, Nick Seymour, Matthieu B\'ethermin, {\bf Sthabile Kolwa}, Bitten Gullberg, and Dominika Wylezalek (2019)\\
\href{http://adsabs.harvard.edu/abs/2019A\%26A...621A..27F}{A\&A, 621, 27} \\
{\it On the road to quenching massive galaxies: ALMA observations of powerful high redshift radio galaxies}\\
 \\
J. Vernet, M. D. Lehnert, C. De Breuck, M. Villar-Mart\'in, D. Wylezalek, T. Falkendal, G. Drouart, {\bf S. Kolwa}, A. Humphrey, B. P. Venemans, and F. Boulanger (2017) \href{http://adsabs.harvard.edu/abs/2017A\%26A...602L...6V}{A\&A; 602, 6} \\
{\it Are we seeing accretion flows in a 250 kpc-sized Ly$\alpha$ halo at $z=3$}  \\
\\
Matt J. Jarvis, A. R. Taylor, I. Agudo, James R. Allison, R. P. Deane, B. Frank, N. Gupta, I. Heywood, N. Maddox, K. McAlpine, Mario G. Santos, A.M. M. Scaife, M. Vaccari, J. T. L. Zwart, E. Adams, D. J. Bacon, A. J. Baker, Bruce. A. Bassett, P. N. Best, R. Beswick, S. Blyth, Michael L. Brown, M. Br\"uggen, M. Cluver, S. Colafranceso, G. Cotter, C. Cress, R. Dav\'e, C.Ferrari, M. J. Hardcastle, C. Hale, I. Harrison, P. W. Hatfield, H.-R. Kl\"ockner, {\bf S. Kolwa}, ...  (2016)\\ 
\href{http://adsabs.harvard.edu/abs/2016mks..confE...6J}{PoS(MeerKAT2016)006} \\
{\it The MeerKAT International GHz Tiered Extragalactic Exploration Survey \\
(MIGHTEE)}  \\

\normalsize{\bf In preparation:}\\
{\bf S. Kolwa}, et al (2019)\\
{\it {Molecular hydrogen kinematics and masses traced by neutral carbon in $z \gtrsim 2.9$ radio galaxies}
