\addcontentsline{toc}{chapter}{\protect Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}


\chapter*{Acknowledgements}

\section*{Official}
The {\bf European Southern Observatory} is noted as the central funding body for this thesis. The {\bf International Max Planck Research Schools (IMPRS)} are recognised for their administrative co-ordination of this project.\\
This thesis makes use of data provided by the {\bf NRAO}: The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc. \\
This thesis is also based on observations made with the {\bf NASA/ESA Hubble Space Telescope}, obtained from the data archive at the Space Telescope Science Institute. STScI is operated by the Association of Universities for Research in Astronomy, Inc. under NASA contract NAS 5-26555.\\
Additionally, this thesis is based [in part] on archival data obtained with the {\bf Spitzer Space Telescope}, which is operated by the Jet Propulsion Laboratory, California Institute of Technology under a contract with NASA. Support for this work was provided by an award issued by JPL/Caltech.\\
This thesis is also based on observations collected at the {\bf European Organisation for Astronomical Research in the Southern Hemisphere} under ESO programme(s) 096.B-0752(A).\\
This thesis makes use of the following {\bf ALMA} data: ADS/JAO.ALMA\#2015.1.00530.S. ALMA is a partnership of ESO (representing its member states), NSF (USA) and NINS (Japan), together with NRC (Canada), MOST and ASIAA (Taiwan), and KASI (Republic of Korea), in cooperation with the Republic of Chile. The Joint ALMA Observatory is operated by ESO, AUI/NRAO and NAOJ.

\section*{Personal}
{\bf Theresa Mareta Kolwa}! Thank you for being the rock that I clung to during all the trials and storms life has presented us. It was seldom easy but you taught us to fight and overcome. My angel, my queen - you are so much stronger than you know. None of this would have been possible without you sowing the seed of possibility in my little ten year old brain. My love for you is colossal. \\
{\bf Lisa, Martin, Lee and Sid} - the best group of older siblings one could ever wish for. You were never easy on me and it built my character (somewhat). {\bf Kennedy Kolwa}! We have never been as close as I wished but I hold dear all the wise words you offered during those rare moments in my life when we spoke earnestly with one another. To {\bf BoMa ba ko Barracks} a.k.a. Aunty Agnes, you showed how to remain compassionate and yet enduring at the same time. Your words of encouragement and praise of my abilities helped me believe during times when I was totally overcome by self-doubt. \\
{\bf Carlos de Breuck and Jo\"el Vernet} - the dream ALMA-MUSE team - thank you for a superb effort in guiding me through this complicated maze to help me find my way out. You invited me into your homes and welcomed me into your academic family. I am very appreciative of the opportunity to work on completing this thesis with your assistance.  \\
To all my {\bf family members in Zambia} - aunts, uncles, cousins, nieces and nephews who I unfortunately almost never get to see - thank you for all the encouragement you sent along the way. \\
To my {\bf LGBTQ friends and acquaintances in Munich}, thank you for holding me up after my coming out, keeping me company during my birthdays and all the wonderful times we have spent laughing, dancing, sharing ideas, career and relationship advice. \\
{\bf Friends and acquaintances at ESO} who were supportive and full of advice who offered great humour and conversation over lunch breaks, and organised outings. Thanks for all the social stuff. You made ESO feel like family. \\
Thank you to all faculty, admin, postdocs and students at the {\bf UCT, UWC Astronomy departments} that offered their advice, insider secrets, guidance, honest criticisms, company, and jokes along the journey toward this pinnacle. I also send a big thanks to {\bf UCT Physics Department}, in particular for the invaluable training and teaching offered that set the foundation I needed to reach this point. \\
Final thank you to the {\bf production team: producer, musicians and engineers} of my first single ``Cosmos" which I perform under the artist name Senanga Kuti. The last couple of months of my thesis were all the more bearable and fun because of this. Thanks! \\
{\bf Live long and prosper!}\\